gij bent 2

### 2025-09-28 paper/paper.qmd
Add caption to boxplot figure

Our influence metric is based on the priming ratio from @sevenants_investigating_2024 and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013]. The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts. Where some users have thousands of followers, some only have a few. The use of the logarithm scales this discrepancy down. In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users. The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`). The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e. users who have more followers than they themselves follow people. This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006; related to the Pareto Principle: @juran_non_1975]. Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users.

```{r #fig-influence}
boxplot(coefficients$influence, horizontal = T)
```

>>>>

Our influence metric is based on the priming ratio from @sevenants_investigating_2024 and hinges on logarithm and Laplace smoothing [@brysbaert_dealing_2013]. The logarithm is a key operation in order to compress the wide numeric range found in follower and following counts. Where some users have thousands of followers, some only have a few. The use of the logarithm scales this discrepancy down. In addition, we use Laplace smoothing in order to avoid division by zero, in the event that users do not follow other users. The mean influence value among our speakers is `r coefficients$influence %>% mean() %>% formatd()` (median `r coefficients$influence %>% median() %>% formatd()`). The boxplot in @fig-influence shows that our dataset generally consists of more influential figures, i.e. users who have more followers than they themselves follow people. This is expected, since broadly speaking, 90% of social media users only read, but never post themselves [@nielsen_participation_2006; related to the Pareto Principle: @juran_non_1975]. Since our dataset consists of posts, it makes sense that our dataset mainly engages with the other 10%, the active users. @fig-influence-boxplot shows the distribution of the influence metric.

```{r #fig-influence}
#| label: fig-influence-boxplot
#| caption: The distribution of the influence metric in our dataset. The bulk of our tweet authors are followed more than they follow others themselves.

boxplot(coefficients$influence, horizontal = T)
```
